---
title: "Building a Model with Categorical Data"
author: "Mehmet ÇAY"
date: '2022-08-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Building a Model with Categorical Data

We have built model with only numeric variables so far. Nor it is time to dive deep and discover Dummy Variables or One Hot Encoding.
I assume you know what is One Hot Encoding and idea underlying it. If not, check [here](https://www.statology.org/one-hot-encoding-in-r/)  

Let's make categorical variables as factor first.

```{r}
data <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Regressions/Regressions/Life Expectancy Data.csv")

levels(data$Country)
levels(data$Year)
levels(data$Status)

data_cat <- data

data_cat$Country <- as.character(data$Country)
data_cat$Country <- as.factor(data$Country)

data_cat$Year <- as.character(data$Year)
data_cat$Year <- as.factor(data$Year)

data_cat$Status <- as.character(data$Status)
data_cat$Status <- as.factor(data$Status)

dataset2=na.omit(data_cat)

set.seed(735)
sampleIndex <- sample(1:nrow(dataset2),size=0.8*nrow(dataset2))
trainSet <- dataset2[sampleIndex,]
testSet <- dataset2[-sampleIndex,]
```
All things are ready. In R, creating categorical model is easy because we do not have to do additional process. All we had to do was identify variables as a factor.
```{r}
modelCat <- lm(Life.expectancy ~. ,data = trainSet)
summary(modelCat)
```
Test Time!
```{r}
predictions <- predict(modelCat,testSet)

library(caret)
R2(predictions,testSet$Life.expectancy)
RMSE(predictions,testSet$Life.expectancy)
MAE(predictions,testSet$Life.expectancy)
```
Results are the best result until now. R2 is almost 1 which is the best for a model. MAE says we can predict life expectancy average ~1 years errors. 
