---
title: "Elastic Net Regression"
author: "Mehmet ÇAY"
date: '2022-08-31'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Elastic Net Regression

Elastic Net Regression basically finds the best line between Ridge Regression and Lasso Regression. If you remember, we gave alpha 0 when we want to do Ridge Regression, 1 for Lasso Regression. Now, Elastic Net Regression finds best alpha value, for instance alpha = .4 may be interpreted 40 percentage of Ridge and 60 percentage of Lasso Regression.

```{r}
library(tidyverse)
library(glmnet)
library(caret)

modelData <- mtcars %>% mutate(
                    cyl = as.factor(cyl),
                    vs = as.factor(vs),
                    am = as.factor(am),
                    gear = as.factor(gear),
                    carb = as.factor(carb)
      )

modelDataDummy <- model.matrix( ~ . , data  = modelData)
View(modelDataDummy)

set.seed(155)
sampleTrainIndex <- sample(1:nrow(modelDataDummy) , size = 0.75*nrow(modelDataDummy))

trainData <- modelDataDummy[sampleTrainIndex , ]
testData <- modelDataDummy[-sampleTrainIndex , ]

trainDataX <- trainData[, -c(1,2)]
trainDataY <- trainData[, 2]

testDataX <- testData[, -c(1,2)]
testDataY <- testData[, 2]

lambdas <- 10^seq(2,-2 , by = -0.01)

modelElastic <- glmnet(trainDataX , trainDataY , alpha = 0.5 , lambda = lambdas)

plot(modelElastic , xvar = "lambda")
```
Elastic Net Cross Validation
```{r echo=TRUE, message=FALSE, warning=FALSE}
trControl = trainControl(method = "repeatedcv" , number = 3 , 
             repeats = 5 , 
             search = "random",
             verboseIter = TRUE , )


modelElasticCV<- train(trainDataX , trainDataY ,  method = "glmnet" , 
                   tuneLength = 30 , 
                   trControl = trControl)

```


Model Performance
```{r}

predictModel <- glmnet(trainDataX , trainDataY , alpha = 0.3638, lambda = modelElasticCV$bestTune )

predictions_1 <- predict(predictModel , testDataX )

caret::R2(predictions_1 , testDataY)
caret::RMSE(predictions_1 , testDataY)
caret::MAE(predictions_1 , testDataY)

```

