---
title: "Ridge Regression"
author: "Mehmet ÇAY"
date: '2022-08-31'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ridge Regression

It is going to be assumed that you have enough theoretical knowledge about Ridge Regression. If not, you can check [here](https://www.youtube.com/channel/UCtYLUTtgS3k1Fg4y5tAhLbw)


However, what we are  going to do is predict loan amount.

```{r}
bank <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Regressions/Regressions/bank.csv", sep="")


library(tidyverse)
data <- bank %>% mutate(income_category=as.factor(income_category),purpose_cat=as.factor(purpose_cat)) %>% select(loan_amount,income_category,purpose_cat,emp_length_int,annual_inc,installment,dti)

```
In Ridge Regression in contrast Multiple Linear Regression we have to make Dummy Variables ourselves. 
```{r}
data2 <- model.matrix(loan_amount~. , data=data)
head(data2)
```
Ridge Model
```{r}
set.seed(264)
sampleIndex <- sample(1:nrow(data2),size=0.8*nrow(data2))
trainSetIndependent <- data2[sampleIndex,]
testSetIndependent <- data2[-sampleIndex,]

trainSetDependent <- data$loan_amount[sampleIndex]
testSetDependent <- data$loan_amount[-sampleIndex]

library(glmnet)

modelRidge <- glmnet(trainSetIndependent,trainSetDependent,alpha=0,lambda=0.1)
summary(modelRidge)
```
In order to find best lambda value, cross validation should be proceed.
```{r}
lambdas <- 10^seq(3,-3,by=-.01)

modelRidgeCV <- cv.glmnet(trainSetIndependent,trainSetDependent,alpha=0,lambda=lambdas,nfolds=5)

plot(modelRidgeCV)
```
As it can be seen in the graph, MSS values are changing according to lambdas value. Min error was signed in the graph.
```{r}
modelRidgeCV$lambda.min

bestModel <- glmnet(trainSetIndependent,trainSetDependent,alpha=0,lambda=modelRidgeCV$lambda.min)

predictions <- predict(bestModel,testSetIndependent)

library(caret)
R2(predictions,testSetDependent)
RMSE(predictions,testSetDependent)
MAE(predictions,testSetDependent)

```
Results are good. We can estimate loan amount average ~2000 error.When the hundreds of thousands are considered , this error is good.
