---
title: "Stepwise Regression"
author: "Mehmet ÇAY"
date: '2022-08-30'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Stepwise Regression

It is used to determine best model with its variables. In fact, we use it when we have a lot of variables and want to decide which one of them we should include.

```{r}
data <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Regressions/Regressions/Life Expectancy Data.csv")

dataset <- data[,c(4:22)] #All numeric variables

library(mice)
md.pattern(dataset)

imputed <- mice(dataset,m=5,method="cart")
dataset2 <- as.data.frame(complete(imputed,m=3))

library(outliers)
scores <- scores(dataset2,type="z",prob=0.95)
anyTrue <- apply(scores,1,FUN=function(x){any(x)})
index <- which(anyTrue)
datasetFinal <- dataset2[-index,]

set.seed(324)
sampleIndex <- sample(1:nrow(datasetFinal),size=0.8*nrow(datasetFinal))
trainSet <- datasetFinal[sampleIndex,]
testSet <- datasetFinal[-sampleIndex,]

```
This codes came from previous document which is Multiple Linear Regression.

```{r}
modelStep <-step(lm(X1.Life.expectancy~1,data=trainSet),direction = "both",scope = ~ X1.Adult.Mortality + X1.infant.deaths+ X1.Alcohol+X1.percentage.expenditure+X1.Hepatitis.B+X1.Measles+X1.BMI+X1.under.five.deaths+X1.Polio+X1.Total.expenditure+X1.Diphtheria+X1.HIV.AIDS+X1.GDP+X1.Population+X1.thinness..1.19.years+X1.thinness.5.9.years+X1.Income.composition.of.resources+X1.Schooling)
```
Method was "both". That means add and remove variables. It used AIC and RSS values to determine whether added or removed variables affect in good way or bad way to our model. Eventually, it finds best model.

```{r}
modelStep
```
That is our best model. Let's test it.
```{r}
bestModel <- lm(formula = X1.Life.expectancy ~ X1.Income.composition.of.resources + 
    X1.HIV.AIDS + X1.Adult.Mortality + X1.Total.expenditure + 
    X1.Schooling + X1.thinness.5.9.years + X1.Alcohol + X1.Diphtheria + 
    X1.Population + X1.thinness..1.19.years + X1.percentage.expenditure + 
    X1.GDP, data = trainSet)
predictions <- predict(bestModel,testSet)

library(caret)
R2(predictions,testSet$X1.Life.expectancy)
RMSE(predictions,testSet$X1.Life.expectancy)
MAE(predictions,testSet$X1.Life.expectancy)
```
Results are better. Our average error is now ~1.5 years. R2 is almost doubled.
